Jaigo Technical Report

### 2007-12-19 trunk/paper/paper.tex
incorporate selected listings

\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{memhfixc}

@@

\tableofcontents
\listoftables

@@

\chapter{Technical details}
%Code Listing
- Implementation of Benson's algorithm for determining unconditional life: Analyze\_Color\_Unconditional\_Status
- Greedy Search algorithm: select\_scored\_move
- Crawler algorithm: select\_crawler\_move

>>>>

\usepackage{listings}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{memhfixc}

@@

\tableofcontents
\listoftables
\lstlistoflistings

@@

\chapter{Technical details}
%Code Listing
\lstset{language=Java,breaklines=true}% if I have extra time, I'll define JavaScript for real
\lstinputlisting[label={code:benson}, caption={Benson's Algorithm}]{benson.js}
\lstinputlisting[label={code:greedy}, caption={Move generator: greedy search}]{greedy.js}
\lstinputlisting[label={code:crawler}, caption={Move generator: crawler}]{crawler.js}
